\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-07-05 cubble.Rmd
conclusion

Possible future directions, other commonly-used spatial or temporal data structures can be integrated into the \pkg{cubble} package to extend analysts' familiar spatial and temporal toolkit to spatio-temporal.

>>>>

Possible future directions would be in two main directions: handling much larger data sets, and integrating smoothly with modeling. Spatio-temporal data can be huge, and the current recommendation is to first reduce the spatial and temporal components before constructing a cubble. Better support could be provided with additional pre-processing functions. Considerable effort has been exerted to provide tidy tools for models, with the \pkg{tidymodels} project. It provides a much better interface to the vast array of statistical and machine learning model architecture. A similar direction would be to extend cubble to provide a more unified interface to spatio-temporal modeling.

### 2023-07-05 cubble.tex
conclusion

The paper includes several examples to illustrate the utility of \pkg{cubble} as a data structure for spatio-temporal analysis. These examples cover different tasks of a typical data analysis workflow involving spatio-temporal data: handling data with spatial and temporal misalignment, matching data from multiple sources, and creating both static and interactive spatio-temporal visualisation. For future directions, other commonly-used spatial or temporal data structures can be integrated into the \pkg{cubble} package to extend analysts' familiar spatial and temporal toolkit to spatio-temporal.

>>>>

The paper includes several examples to illustrate how \pkg{cubble} is useful for spatio-temporal analysis. These examples cover different tasks of a typical data analysis workflow: handling data with spatial and temporal misalignment, matching data from multiple sources, and creating both static and interactive graphics. In addition, a re-working of an existing climate reanalysis using cubble is explained.

Possible future directions would be in two main directions: handling much larger data sets, and integrating smoothly with modeling. Spatio-temporal data can be huge, and the current recommendation is to first reduce the spatial and temporal components before constructing a cubble. Better support could be provided with additional pre-processing functions. Considerable effort has been exerted to provide tidy tools for models, with the \pkg{tidymodels} project. It provides a much better interface to the vast array of statistical and machine learning model architecture. A similar direction would be to extend cubble to provide a more unified interface to spatio-temporal modeling.
